---
title: "BASC Different samples & Regressors"
author: "Raúl RC"
date: "February 2, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, echo=FALSE, warning=FALSE, message=FALSE}
library(dendextend)
library(corrplot)
setwd("/misc/ernst/rcruces/git_here/micasoft/sandbox/raul/BASC")

# FUNCTION: Read the bootstraped data
read.basc <- function(Path){
  # Loads the data
  load(Path)
  # Stabilization of the Final Sij_Boot matrix
  Sij <- k10$Sij/k10$N
  Sij <- Sij/max(Sij)
  # Euclidean distance matrix
  vec <- rownames(Sij)
  d <- dist(Sij,method = "euclidean")
  # Hierarchical Agglomerative Clustering: Ward D
  hc <- hclust(d,method = "ward.D",members = vec)
  #hc.dend <- as.dendrogram(hc)
  # Get best partition from k10$k
  K <- as.numeric(names(table(k10$k)[match(max(table(k10$k)),table(k10$k))]))
  clusterBest <- cutree(hc, K)
  return(list(Sij=Sij, hc=hc, clusterBest = clusterBest))
}

# FUNCTION: Compares two hclust objects
comp.clust <- function(hc1, hc2){
  # Compares two hclust objects, is the subjects are the same
  dend.obj1 <- as.dendrogram(hc1)
  dend.obj2 <- as.dendrogram(hc2)
  # Modify the dendrogram to have cluster-based colors in the branches and labels
  Col <- c("darkgoldenrod2","darkblue","seagreen")
  dend.obj1 <- dend.obj1 %>% 
    # color_branches(dend.obj1,col=Col,k=3) %>% 
    # color_labels(dend.obj1,col=Col,k=3) %>% 
    set("branches_lwd", 3)
  dend.obj2 <- dend.obj2 %>% 
    # color_branches(dend.obj2,col=Col,k=3) %>% 
    # color_labels(dend.obj2,col=Col,k=3) %>% 
    set("branches_lwd", 3)
  # Baker's Gamma Index
  print(paste("Baker's Index:",cor_bakers_gamma(dend.obj1,dend.obj2)))
  # Entanglement
  print(paste("Entanglement:",entanglement(dend.obj1,dend.obj2)))
  # Plot the edges differences
  dend_diff(dend.obj1, dend.obj2)
  # Create a list of dendrograms and a plots the tanglegram
  dend.ls <- dendlist(dend.obj1, dend.obj2)
  # Plot the tanglegram
  tanglegram(dend.ls,common_subtrees_color_branches = TRUE)
}

# FUNCTION: barplot of the model's best partition
plot.clust <- function(clust.best, Main){
  clust.best <- table(clust.best)
  # Function to plot the number of observations per stack
  plot.n <- function(Values,y.pos,Space) {
    labs<- paste(Values, sep="")
    text(seq(from=0.5+Space,by = 1+Space,length.out = length(Values)),y.pos,labs, col="white",cex=1.5)}
  # Barplot of the clusters
  Space=0.05
  Col <- c("darkgoldenrod2","seagreen","darkblue")
  barplot(clust.best,space = Space,col = Col, border = Col, main= Main)
  plot.n(clust.best, clust.best/2,Space)
}

# FUNCTION plot lines and dots from Sij
cluster.test <- function(Sij, Main) {
  source("/misc/ernst/rcruces/git_here/micasoft/sandbox/raul/BASC/functions.R")
  source("/misc/ernst/rcruces/git_here/micasoft/sandbox/raul/BASC/BASC_func.R")
  par(mfrow=c(1,3))
  # Calculo de la matriz de distancias euclidenanas
  vec <- rownames(Sij)
  d <- dist(Sij,method = "euclidean")
  # Método de Cluster
  hc <- hclust(d,method = "ward.D",members = vec)
  hc.dend <- as.dendrogram(hc)
  # Color the first sbranch in golden... the second sub-branch in green and the second sub-branch  in blue
  colbranches <- function(n, col) {
    a <- attributes(n) # Find the attributes of current node
    # Color edges with requested color
    attr(n, "edgePar") <- c(a$edgePar, list(col=col, lwd=2))
    n }
  hc.dend[[1]] = dendrapply(hc.dend[[1]], colbranches, "darkgoldenrod2")
  hc.dend[[2]][[2]] = dendrapply(hc.dend[[2]][[2]], colbranches, "seagreen")
  hc.dend[[2]][[1]] = dendrapply(hc.dend[[2]][[1]], colbranches, "darkblue")
  # Dendrogram
  #plot(hc.dend,xlab="",main=Main,col.main="black",cex.main=3,col="black",lwd=4,axes = TRUE,ylab="High", horiz = TRUE)
  # -------------------------------------------------------------- #
  # Load data
  load.npsy <- function() {
    source("/misc/ernst/rcruces/git_here/micasoft/sandbox/raul/BASC/functions.R")
    source("/misc/ernst/rcruces/git_here/micasoft/sandbox/raul/BASC/BASC_func.R")
    Npsy <- read.csv("/misc/ernst/rcruces/git_here/micasoft/sandbox/raul/BASC/neuropsy.csv")
    Npsy.z <- Npsy[,c("urm","group","IQ","VCI","PR","PS","WMI","VMI","VWMI","IMI","DMI","AMI")]
    # Create a Z-score based on controls for each cognitive variable
    controls <- which(Npsy.z$group == "ctrl")
    Npsy.z[,3:12] <- apply(Npsy.z[,3:12], 2, function(x) Zscore(x[controls],x))
    return(Npsy.z)
  }
  #### Blank Plot ####
  blank.plot <- function (x,lab,Main,pts) {
  Ax.Col="black"
  Main <- as.character(Main)
  plot(rep(1,length(pts[[1]][,1])),pts[[1]][,1],ylim=c(-8,4),xlim = c(0,max(x)+1),pch=19,ylab="Z-score",main=Main,col=NA,xaxt='n',bty='n',xlab="",axes = FALSE,
       las=1,col.axis=Ax.Col,col.lab=Ax.Col,col.main=Ax.Col,cex.axis=1.2,cex=seq(0.5,1.5,length.out = 35),cex.main=3)
  axis(1, at=x, col.axis=Ax.Col,labels=lab, lty=1, col=Ax.Col, las=1,lwd=3,cex.axis=1,col.lab=Ax.Col)
  axis(2, at=seq(-8,4,4), labels=seq(-8,4,4), lty=1, col.axis=Ax.Col,las=1,lwd=3,cex.axis=1.2,col.lab=Ax.Col,col=Ax.Col)
  abline(h=c(-2,0,2),col=addTrans(Ax.Col,30),lty=4,lwd=3)
  mtext("WAIS",side = 1,at = 3,cex = 1.5,col=Ax.Col,line = 3)
  mtext("WMS",side = 1,at = 9,cex = 1.5,col=Ax.Col,line = 3)}

  # -------------------------------------------------------------- #
  # Plots of each cluster
  # Selecciona solo 3 clusters
  cases <- load.npsy()
  clusterBest <- cutree(hc, 3)
  clust.ID<-as.data.frame(cbind(clusterBest,names(clusterBest)))
  colnames(clust.ID)<-c("clust","urm")
  cases <- merge(cases,clust.ID,by="urm")
  x <- 1:10
  len <- length(cases)
  pts <- list(cases[,3:12])
  lab <- colnames(cases[,3:12])
  blank.plot(x,lab,paste(Main,"1"),pts)
  plotLines(cases[cases$clust == "1",][3:12],"darkgoldenrod2",x)
  blank.plot(x,lab,"Cluster 2",pts)
  plotLines(cases[cases$clust == "2",][3:12],"seagreen",x)
  blank.plot(x,lab,"Cluster 3",pts)
  plotLines(cases[cases$clust == "3",][3:12],"darkblue",x)
}
```

# BASC Robustness  
  
## BASC robustness: Same sample  
Testing the clustering similarity of the 34 subjects sample runned twice.
```{r robustness, echo=FALSE}
comp.clust(read.basc("models/10k_34subjs.RData")$hc,read.basc("models/10k_34subjs_B.RData")$hc)
```

## BASC Robustness: Same sample + laterality 
Testing the clustering similarity of the 34 subjects: One sample WAIS and WMS indexes, the  other adding  laterality .
```{r, echo =FALSE, warning=FALSE}
comp.clust(read.basc("models/10k_34subjs.RData")$hc,read.basc("models/10k_34subjs_LAT.RData")$hc)
```

## BASC robustness: Laterality flipped
Testing the clustering similarity of the 34 subjects: One sample WAIS and WMS indexes with laterality coded for both left -1 and 1.
```{r, echo =FALSE, warning=FALSE}
comp.clust(read.basc("models/10k_34subjs_LAT.RData")$hc,read.basc("/misc/ernst/rcruces/git_here/epilepsia_processing/databases/basc_latFLIP.RData")$hc)
```

  
## Stability Matrices: Only Index & Index + Laterality  
```{r, echo =FALSE, warning=FALSE}
library(corrplot)
par(mfrow=c(1,2))
# Color palette
colC <- colorRampPalette(c("gold","darkgoldenrod2","seagreen","royalblue4","white","white","white","royalblue4","seagreen","darkgoldenrod2","gold"))
# Plot Stability matrix
obj <- corrplot(read.basc("models/10k_34subjs.RData")$Sij,order="hclust",tl.col="black",method="color",addgrid.col=NA,col=colC(100),is.corr = FALSE,cl.lim = c(0,1))
ord <- colnames(obj)
# Objects with the model with laterality
basc.lat <-  read.basc("models/10k_34subjs_LAT.RData")$Sij
idx <- match(ord,colnames(basc.lat))
try(corrplot(basc.lat[idx,idx],tl.col="black",method="color",addgrid.col=NA,col=colC(100),is.corr = FALSE,cl.lim = c(0,1)))
```

# BASC: Distribution of the number of Clusters  
```{r Nclusters, echo=FALSE, fig.height=8, fig.width=13}
setwd("/misc/ernst/rcruces/git_here/micasoft/sandbox/raul/BASC/models")
# READ ALL DATA
# I removed the repeated models and the ones that are very very bad
files <- list.files(pattern = "10k_")[-c(17,8)]
# Reorder for better visualization of barplots
files <- files[c(1:7,19,8:18,20:21)]
noms <- sapply( strsplit( sapply(strsplit(files, split='10k_', fixed=TRUE), function(x) (x[2])), split = ".RData"), function(x) (x[1]))

# Clusterization distribution
func.test <- function(Path, Name){
   k10 <- read.basc(Path)
   plot.clust(k10$clusterBest, Main= Name)}
par(mfrow=c(3,7))
for (i in 1:length(files)) {func.test(files[i],noms[i])}

# Compares 34 subject sample vs 34 subjects sample+AGE
#comp.clust(read.basc("10k_34subjs_age.RData")$hc,read.basc("10k_34subjs.RData")$hc)
# Compares 33 subject+EDU+HS sample vs 33 subjects sample+EDU
#comp.clust(read.basc("10k_33subjs_edu-hs.RData")$hc,read.basc("10k_33subjs_edu.RData")$hc)

```

# BASC: Distribution of the number of Clusters 
```{r matrices, echo=FALSE, warning=FALSE, message=FALSE, fig.height=6, fig.width=6}
setwd("/misc/ernst/rcruces/git_here/micasoft/sandbox/raul/BASC/models")
# DATA MATRIX OF SUBJECT X MODEL
subjs2mtx <- function(N){
  N <- as.character(N)
  # Creates the data frame
  clusters <- data.frame(as.integer(names(read.basc(files[grep(N,files)][1])$clusterBest)))
  # Data frame's names
  colN <- "urm"
  # Reads every clusterization
  for (i in grep(N,files)) {
    k10 <- read.basc(files[i])
    clusters <- cbind(clusters, k10$clusterBest)
    colN <- c(colN, noms[i]) }
  # Column's names
  colnames(clusters) <- colN
  return(clusters)
}
# Merges all clusters in one matrix
basc.models <- merge(subjs2mtx(34),subjs2mtx(33),by="urm", all=TRUE)
basc.models <- merge(basc.models, subjs2mtx(31),by="urm", all=TRUE)
# Adding IQ for sorting
basc.models <- merge(read.csv("/misc/ernst/rcruces/git_here/micasoft/sandbox/raul/BASC/neuropsy.csv")[,c(1,8)],basc.models, by="urm")
basc.models$IQ <- as.numeric(scale(basc.models$IQ))
# NA to zero for plotting
basc.models[is.na(basc.models)] <- 0
# Rownames as ID
rownames(basc.models) <- basc.models$urm

#### OHBM sample vs BASC: ROBUSTNESS #### 
# s31.ohbm <- read.csv("/misc/ernst/rcruces/Dropbox/linuxook/oma/cases_Zclust.csv")
# s31.ohbm <- s31.ohbm[s31.ohbm$clust !=0,c(20,9)]
# colnames(s31.ohbm) <- c("urm","s31.ohbm")
# s31.ohbm <- merge(basc.models[c(1,22)],s31.ohbm,by="urm")
# s31.ohbm[2] == s31.ohbm[3]
# CONCLUSION: IS SUPER REPRODUCTIBLE aka THE SAME

# Agroup per model for visualization purposes
basc.models <- basc.models[c("urm","IQ","34subjs_LAT","31subjs_ohbm","34subjs",
                             "33subjs_age","31subjs_age","34subjs_age",
                              "33subjs",
                              "34subjs_sex","33subjs_sex","31subjs_sex",
                              "34subjs_edu","33subjs_edu","31subjs_edu",
                              "34subjs_edu-hs","33subjs_edu-hs","31subjs_edu-hs",
                              "34subjs_age-edu-sex-hs","31subjs_age-edu-sex-hs",
                              "34subjs_hs","33subjs_hs","31subjs_hs")]

# VISUALIZATION OF DATA MATRIX OF SUBJECT X MODEL
# Sorted from Lower to higher IQ
library(corrplot)
colC <- colorRampPalette(c("white","white","white","white","forestgreen","darkblue","red"))
corrplot(as.matrix(basc.models[order(basc.models$IQ),3:23]),is.corr = FALSE,method = "color",col=colC(100),tl.col="black",addgrid.col = NA,cl.pos = "n")
# Heat map of basc models with dendrograms
library(gplots)
heatmap.2(as.matrix(basc.models[order(basc.models$IQ),3:23]),trace="none",dendrogram='both',Rowv=TRUE,Colv=TRUE,col=c("forestgreen","darkblue","red"),main = "Clusters clusterized")
```


# BASC: Distribution between n=34 
```{r echo=FALSE,warning=FALSE,message=FALSE,fig.height=4, fig.width=12}
setwd("/misc/ernst/rcruces/git_here/micasoft/sandbox/raul/BASC/models")
# BARPLOT of each subjects distribution
par(mfrow=c(1,4))
for (i in c(20,8,6)) {func.test(files[i],noms[i])}
func.test("/misc/ernst/rcruces/git_here/epilepsia_processing/databases/basc_latFLIP.RData","Lateralized Flipped")
# basc models
basc.hbm <-  read.basc("10k_31subjs_ohbm.RData")$Sij
basc.n34 <-  read.basc("10k_34subjs.RData")$Sij
basc.flp <-  read.basc("/misc/ernst/rcruces/git_here/epilepsia_processing/databases/basc_latFLIP.RData")$Sij

# Lines and dots 
cluster.test(basc.hbm,"n=31 OHBM sample")
cluster.test(basc.lat,"n=34 with Lateralization")
cluster.test(basc.lat,"n=34 with Lateralization Flipped")
cluster.test(basc.n34,"n=34 WAIS & WSM")
```